Figures

### 2019-07-09 figures/07_model-selection.Rmd
add map to makefile

gg_tp <- ggplot(data = dt) + 
  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tn, y = tp, color = signif_hu4)) +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) + 
  theme(rect = element_rect(fill = "transparent"))

>>>>

gg_tp <- ggplot(data = dt) + 
  geom_point(aes(x = tp, y = tn, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tp, y = tn, color = signif_hu4)) +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) + 
  theme(rect = element_rect(fill = "transparent"))

### 2019-07-09 manuscript/figures.Rmd
add map to makefile

```{r maps, fig.cap = "Quanitle map of lake nutrients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

>>>>

```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

```{r maps2, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/11_map-1.pdf")
```
